---
title: "Workings - Daily News for Stock Market Prediction"
output: html_notebook
---

# Import libraries
```{r}
library(ggplot2)
library(magrittr)
```

# Import data
```{r}
library(readr)
<<<<<<< HEAD
comb.df <-
  read_csv(
  "D:/Code/R/Kaggle/stocknews/Data/Combined_News_DJIA.csv",
  col_types = cols(Label = col_factor(levels = c("0",
  "1")))
  )
  
djia.df <- read_csv("D:/Code/R/Kaggle/stocknews/Data/DJIA_table.csv")
reddit.df <- read_csv("D:/Code/R/Kaggle/stocknews/Data/RedditNews.csv")
```
The combined dataset has `r nrow(comb.df)` rows and `r ncol(comb.df)` columns.

Summary of all 3 datasets:
```{r}
summary(comb.df)
summary(djia.df)
summary(reddit.df)
```



# Data Exploration

## News
View a selection of the Top 1 news:
```{r}
 comb.df %>%
=======
djia.df <- read_csv("D:/Code/R/Kaggle/stocknews/Data/Combined_News_DJIA.csv", 
    col_types = cols(Label = col_factor(levels = c("0", 
        "1"))))
summary(djia.df)
```
The dataset has `r nrow(djia.df)` rows and `r ncol(djia.df)` columns.

# Data Exploration
View a selection of the Top 1 news:
```{r}
 djia.df %>%
>>>>>>> d7b9c9963676a8179a12265061ebb5c7600719ba
  dplyr::select(Top1) %>%
  dplyr::sample_n(20) %>%
  purrr::map(print)
```
<<<<<<< HEAD
#DJIA

Plot the DJIA closing price:
```{r}
ggplot(djia.df, aes(x = Date, y = `Adj Close`)) +
  geom_line()
```
Study the distribution of the daily returns:
```{r}
daily.rets <- xts::xts(djia.df$`Adj Close`, djia.df$Date) %>% 
  quantmod::dailyReturn()  %>%
  tidyquant::as_tibble(preserve_row_names = T)

colnames(daily.rets) <- c("Date", "Daily Returns")

daily.rets %<>%
  dplyr::mutate(Date = lubridate::ymd(Date))

summary(daily.rets)
```

Days where returns where at the bottom 10%:
```{r}
daily.rets %>%
  dplyr::filter(`Daily Returns`  <= quantile(.$`Daily Returns`, 0.1)) %>%
  dplyr::arrange(Date)
```
=======
>>>>>>> d7b9c9963676a8179a12265061ebb5c7600719ba

